---
title: "Week 7 Assingment"
author: "Ione Arbilla"
date: "13/11/2021"
output:
  html_document:
    df_print: paged
---
## Importing dataset

Reading csv file in  a Dataset obtained from Jobs dataset in https://data.worldbank.org/ and not importing lines located at the end of the document with the filter function.


```{r setup,include=FALSE,echo=FALSE}
library(dplyr)
Dataset<-read.csv("Jobs_Database_Dataset.csv")%>%
  filter(row_number() <= n()-5)
```
## Diagnose of the dataset

This dataset  is wide formatted data, so we will need some pivoting. I created a variable called year to address the problem. I also decided to use parse_number to get rid of the leters and extra numbers that made difficult to read the years. Then I mutated the value column to identify the NA values as NA insetad of ".." and converted it to numeric, since the column is indeed numeric. Finally I altered the column names, round the decimals of the value columns and made a selection of the dataset that i believe could be adequate to compare the indices of two different countries:

```{r cars,echo=FALSE,include=FALSE}
library(tidyr)
library(rlang)
library(readr)


Dataset%>%
  pivot_longer(`X2011..YR2011.`:`X2016..YR2016.`,names_to = "year")%>%
  mutate(year=parse_number(year))%>%
  mutate(value=na_if(value,".."))%>%
  mutate(value=as.numeric(value))%>%
  select(ï..Country.Name, Series.Name,year,value)%>%
  set_names(c("Country","Indices","Year","Value"))%>%
  mutate(across(where(is.numeric), round, 1))%>%
  filter((Country=="Afghanistan"& Year == 2011)|(Country=="Burundi"& Year == 2011))%>% 
  write.csv("Table.csv")

```
```{r,echo=FALSE}
Table<-read.csv("Table.csv")
Table

```

### Including Plots
 Here I added the plots that compare the indices of the selected countries in the year 2011 except of one index which was in a different unit.
 
 <p>&nbsp;</p>                                                                                                                                                                                              

```{r pressure, echo=FALSE}
library(ggplot2)
Table<-read.csv("Table.csv")

ggplot(subset(Table, Indices %in% c("Access to electricity (% of population)",
"Adolescent fertility rate (births per 1,000 women ages 15-19)",
"Age dependency ratio (% of working-age population)",
"Agriculture, value added (% of GDP)",
"Agriculture, value added (annual % growth)"))) +
geom_col(aes(x=Country,y=Value,fill=Indices,group=Indices),position="dodge")+theme_light()

```
<p>&nbsp;</p>                                                                                                                                                                                              

